### 2023-05-27 paper/Chapters/Chapter2.tex
WIP

@@

>>>>

There are also other calibration patterns, some of which are not square (for
example, Delitlle~\citep{haDeltilleGridsGeometric2017}).

@@

\section{Boards' features detection}\label{sec:boards_features_detection}

The detection of the calibration board's features is a crucial step in the
camera calibration pipeline. The detection accuracy directly affects the
calibration accuracy. Besides the feature detection, it's also important to
associate the detected features with the board's corners.

There are various of the feature detection methods. Many of them require
prior knowledge of the board's geometry, such as the number of rows and columns,
and require the full visibility of the board. For example, the default OpenCV
implementation of the chessboard detection~\citep{OpenCVCameraCalibration}.

Because of that, other methods were proposed, such as
\cite{fuersattelOCPADOccludedCheckerboard2016} and
\cite{geigerAutomaticCameraRange2012}. Those method can detect the board under
the partial occlusion and do not require prior knowledge of the board's geometry.
